---
title: "Optimizing common utility Functions"
author: "Diógenes Cruz Figueroa García"
date: "8/3/2020"
output: 
     ioslides_presentation:
          widescreen: TRUE
          smaller: TRUE
          keep_md: yes
     
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Utility Functions

In Economics, it is common to have to maximize utility functions subject to 
some budget constraint, and find the optimal consumption basket.

With the traditional chalkboard, it is somewhat hard to convey the idea of what 
happens when prices or income changes.

The idea with this shiny app is to make it more interactive to students to see 
what happens to optimal consumption baskets when parameters change.

## Setting the app

To see how an optimal utility basket plot looks, let's create some data using 
a simple cobb douglas function:

```{r PlottingCD, warning = FALSE, message = FALSE, comment = FALSE, echo = TRUE, fig.width=4, fig.height=4, fig.align = "center"}
x <- 1:200
y <- 2500/x
plot(x, y, col = "blue", type = "l", xlim = c(0, 200), 
     ylim = c(0, 200), lwd = 2)
points(50, 50, cex = 2, pch = 19)
lines(x, 100 - x, col = "red", lwd = 2)

```

## Justifying the APP

Having to plot many times in the chalkboard several plots is inconvenient, for 
sometimes they are not symetrical, and you cannot see slowly how the plot changes
as the parameter change.

A shiny app can simulate the numbers of several functions, plot them, and allow 
the user to manipulate the parameters to look at changes in the optimal consumption 
basket right at the moment.

## Shiny App Interface
The interface is really straight forward, with a side panel to change the parameters, 
and a main panel with the plot sensible to changes in the parameters.

The interface has a side panel to control the function parameters, such as the 
preference weight and the elasticity of substitution.

The side panel can also control the prices and income for the budget constraint.

[Click here to go the the app](https://diogenescfg.shinyapps.io/DevDataProducts_Assignment/)
